
\renewcommand\bibname{Bibliography}

\begin{thebibliography}{9}
\addcontentsline{toc}{chapter}{Bibliography} % to add it to the tables of contents
% TODO: date de consultation websites
%---------------------chap1
\bibitem[1] {R6}
Wikipedia. URL: \url{https://en.wikipedia.org/wiki/Digitization}

\bibitem[2] {R7}
SmartLab Solutions GmbH website. URL: \url{https://www.smartlab-solutions.de/}

\bibitem[3]{R8}
SmartLab Solutions GmbH Introduction - Präsentation.

\bibitem[4]{R9}
Qualitätsmanagementhandbuch der SmartLab Solutions GmbH.

\bibitem[5]{R10}
Attlassian website. URL: \url{https://www.atlassian.com/agile}

\bibitem[6]{R11}
Wikipedia. URL: \url{https://en.wikipedia.org/wiki/CAN\_bus}

\bibitem[7]{R12}
Texas Instruments article. URL: \url{https://www.ti.com/lit/an/sloa101b/sloa101b.pdf?ts=1693476287427}

\bibitem[8]{R13}
Raspberry Pi website. URL: \url{https://www.raspberrypi.com/products/raspberry-pi-4-model-b/}

\bibitem[9] {R4}
STM32F303RE datasheet. URL: \url{https://www.st.com/resource/en/datasheet/stm32f303re.pdf}

\bibitem[10]{R14}
NUCLEO-F303RE User Manual. URL: \url{https://www.st.com/resource/en/user\_manual/um1724-stm32-nucleo64-boards-mb1136-stmicroelectronics.pdf}

\bibitem[11]{R15}
STM32CubeIDE website. URL: \url{https://www.st.com/en/development-tools/stm32cubeide.html}

\bibitem[12]{R16}
STM32CubeMX website. URL: \url{https://www.st.com/en/development-tools/stm32cubemx.html}

\bibitem[13]{R17}
STM32CubeMonitor website. URL: \url{https://www.st.com/en/development-tools/stm32cubemonitor.html}

\bibitem[14]{R18}
STM32CubeProgrammer website. URL: \url{https://www.st.com/en/development-tools/stm32cubemonitor.html}

\bibitem[15]{R19}
Waveshare website. URL: \url{https://www.waveshare.com/wiki/RS485\_CAN\_HAT}

\bibitem[16]{R20}
MCP2515 datasheet. URL: \url{https://www.waveshare.com/w/upload/8/83/MCP2515.pdf}

\bibitem[17]{R21}
\texttt{can-utils} GitHub repository. URL: \url{https://www.waveshare.com/w/upload/8/83/MCP2515.pdf}

\bibitem[18]{R22}
MCP2551 Micochip website. URL: \url{ https://www.microchip.com/en-us/product/mcp2551#document-table}

\bibitem[19] {R5}
STM32F303RE reference manual, 31 Controller area network (bxCAN), bxCAN functional description, Bit timing, Figure 397, p. 1027. URL: \url{https://shorturl.at/puD67}

\bibitem[20] {R23}
STM32F303RE reference manual, 31 Controller area network (bxCAN), Test mode, Loop back mode, p. 1016. URL: \url{https://shorturl.at/puD67}

\bibitem[21]{R24}
Official Documentation: POSIX pthread.h Header File Specification. URL: \url{https://pubs.opengroup.org/onlinepubs/7908799/xsh/pthread.h.html}

\bibitem[22]{R25}
Wikipedia. URL: \url{https://en.wikipedia.org/wiki/MQTT}

\bibitem[23] {R1}
paho.mqtt.c library. URL: \url{https://github.com/eclipse/paho.mqtt.c}

\bibitem[24] {R2}
paho.mqtt.cpp library. URL: \url{https://github.com/eclipse/paho.mqtt.cpp}

\bibitem[25]{R26}
Wikipedia. URL: \url{https://en.wikipedia.org/wiki/JSON}

\bibitem[26]{R3}
nlohmann/json library. URL: \url{https://github.com/nlohmann/json}

\bibitem[27]{R27}
FreeRTOS website. URL: \url{https://www.freertos.org/index.html}

\bibitem[28]{R28}
STM32F303RE reference manual, 21 General-purpose timers (TIM2, TIM3, TIM4) and 23 General-purpose timers (TIM15, TIM16, TIM17). URL: \url{https://shorturl.at/puD67}

\bibitem[29]{R30}
SysGCC website, aarch64-linux-gnu toolchain. URL: \url{https://gnutoolchains.com/raspberry64/}

\bibitem[30]{R31}
Wikipedia. URL: \url{https://en.wikipedia.org/wiki/Cross_compiler}

\bibitem[31]{R29}
KiCad official website. URL: \url{https://www.kicad.org/}

\bibitem[32]{R32}
Pcbcart website. URL: \url{https://www.pcbcart.com/}

\bibitem[33]{R33}
Digikey website. URL: \url{https://www.digikey.de/}

\bibitem[34]{R34}
Mouser website. URL: \url{https://www.mouser.de/}

\bibitem[35]{R35}
Würth Elektronik website. URL: \url{https://www.we-online.com}

\end{thebibliography}